---

title: "Task1"

author: "Martin Hvizdoš"

date: "10/01/2024"

format: 
  html:
    embed-resources: true

html:

embed-resources: true

editor: source

---

\## Task 5: Visualization

Using the dataset from \*\*Task 4.2\*\* (\`airbnb.csv\`), create \*\*four visualizations\*\* using both the \*\*base plotting system\*\* and \*\*ggplot2\*\*. You may use arbitrary subsets of the data for this task. Ensure that all visualizations include:\\

\- A title,\\

\- Annotated axes,\\

\- A legend (if needed).

\### Instructions:

1.\*\*Histogram\*\*:\\

Create a histogram using the \`hist\` function from the \*\*base plotting system\*\*.

2.\*\*Scatter Plot\*\*:\\

Create a scatter plot using \*\*ggplot2\*\* with the \`geom_point\` geometry. Incorporate a third variable by using different colors to represent it.

3.\*\*Boxplot\*\*:\\

Create a boxplot using \*\*ggplot2\*\* with the \`geom_boxplot\` geometry.

4.\*\*Custom Plot\*\*:\\

Create an additional plot of your choice using either the \*\*base plotting system\*\* or \*\*ggplot2\*\*.

```{r}
file_path <-  "C:/Users/zuzan/Desktop/airbnb_data/amsterdam_weekdays.csv"
file_path <-  "C:/Users/zuzan/Desktop/airbnb_data/amsterdam_weekends.csv"
file_path <-  "C:/Users/zuzan/Desktop/airbnb_data/barcelona_weekends.csv"
file_path <-  "C:/Users/zuzan/Desktop/airbnb_data/barcelona_weekdays.csv"

# Načítanie datasetu z Task 4.2
airbnb_data <- read.csv("airbnb.csv")

# Histogram cien (realSum) - Base R
hist(
  airbnb_data$realSum,
  breaks = 50,
  col = "skyblue",
  main = "Histogram of Airbnb Prices",
  xlab = "Price (realSum)",
  ylab = "Frequency"
)

```

```{r}

# Scatter plot - Base R
plot(
  airbnb_data$guest_satisfaction_overall, 
  airbnb_data$realSum, 
  main = "Scatter Plot of Prices vs Guest Satisfaction",  # Titul
  xlab = "Guest Satisfaction (overall)",  # Popis osi X
  ylab = "Price (realSum)",  # Popis osi Y
  col = as.factor(airbnb_data$city),  # Rôzne farby podľa mesta
  pch = 16,  # Typ bodu
  cex = 0.5  # Veľkosť bodov
)

# Pridanie legendy
legend("topright", legend = levels(as.factor(airbnb_data$city)), 
       col = 1:length(levels(as.factor(airbnb_data$city))), 
       pch = 16, title = "City")

```

```{r}
# Boxplot cien podľa mesta - Base R
boxplot(
  realSum ~ city, 
  data = airbnb_data, 
  main = "Boxplot of Airbnb Prices by City",  # Titul
  xlab = "City",  # Popis osi X
  ylab = "Price (realSum)",  # Popis osi Y
  col = "lightblue",  # Farba boxplotu
  border = "darkblue"  # Farba okrajov
)

```

```{r}
# Filtrácia dát na pracovné dni a víkendy
weekend_data <- airbnb_data[airbnb_data$day_type == "weekends", ]
weekday_data <- airbnb_data[airbnb_data$day_type == "weekdays", ]

# Hustotný graf - Base R
plot(density(weekend_data$realSum), 
     main = "Density Plot of Airbnb Prices (Weekdays vs Weekends)",  # Titul
     xlab = "Price (realSum)",  # Popis osi X
     ylab = "Density",  # Popis osi Y
     col = "blue",  # Farba pre víkendy
     lwd = 2)  # Hrúbka čiary
lines(density(weekday_data$realSum), col = "red", lwd = 2)  # Červená čiara pre pracovné dni

# Pridanie legendy
legend("topright", legend = c("Weekends", "Weekdays"), col = c("blue", "red"), lwd = 2)

```
